---
title       : The ACME car super seller
subtitle    : Maximise your earning potential
author      : James Longman
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 

<h2 style="color:#000000;">Sell more efficeintly</h2>

Our <span style="font-weight:bold; color:#ff0000">patented</span> tool is designed to help you <span style="font-weight:bold; color:#ff0000">maximise</span> your selling potential.

Handles the unique requirements of each customer and guides them to a short list of cars quickly and easily.
</span>

--- .class #id bg:#ccccff

<h2 style="color:#000000;">Simplicity in design</h2>

Fool proof user interface means no delay and <span style="font-weight:bold; color:#ff0000">no looking foolish</span>.

We know you hate computers and couldn't tell one end of a website from your own armpit which is why this tool is designed to be so easy to use you won't even realise just how sophisticated it is behind the scenes.

Using just a simple multi-select input all the power of the tool is unleashed.  Just let the customer choose from the following options.

``` {r, echo=FALSE}

colnames(mtcars)

```

--- .class #id

<h2 style="color:#000000;">Targetted upselling to maximise your revenue</h2>

The tool returns a list of desirable vehicles in a manner that intuitively guides the customer to a higher specification of car.

Only those with above average values for the desired specs are shown thus naturally giving the customer what they requested and removing the chance of a low-spec purcahse

e.g. If the customer decides to choose horse power and weight then:
``` {r, echo=FALSE}

mtcars[mtcars$hp > mean(mtcars$hp) & mtcars$wt > mean(mtcars$wt) ,]

```

--- .class #id bg:#ccccff 

<h2 style="color:#000000;">Clear results, clear profits</h2>

The <span style="font-weight:bold; color:#ff0000">clarity of results</span> shown by the tool means you <span style="font-weight:bold; color:#ff0000">can't fail</span> to seal the deal.

Our patented algorithmic system gives your customer belief they are in control and you that luxuary trip to the Maldives that you've always craved.

Buy smart.  Buy ACME.

